---
title: "Replication of the data analysis in Study1 by Troy et al. (2017) with an Iranian sample."
author: "Alimohammad Soufizadeh"
date: "March, 2022"
---

# Load Packages
```{r}
pacman::p_load(pacman, tidyverse, kableExtra, psych, janitor, car, performance, 
               see,gridExtra, interactions, devtools,rmarkdown, 
               knitr, patchwork, readxl,papaja, jtools)
```


```{r}
# save the excel file as a dataframe named "all_data"
raw_data <- read_excel("Coded_data.xlsx")
```

```{r}
# Change column names
raw_data <- rename(raw_data, 
                   "duration" = "Duration(Second)",
                   "gender" = "Sex")
```

# Raw data
```{r}
# summarise raw data
summary(raw_data)
```

# Exclusion crtieria
- Based on Troy et al's (2017) criteria
```{r}
# 1. exclude all who didn't complete the survey or had missing data
no_missing <- drop_na(raw_data)
```

```{r}
# 2. exclude participants with zero variance among their answers
no_zero_var <- no_missing[apply(no_missing[, -c(1:4)], 1, var) != 0, ]
```

```{r}
# 3. exclude participants who took less than 3 minutes (180 seconds) to complete the survey
clean_data <- no_zero_var %>% filter(duration >= 180)
```

```{r}
# Check for duplicates
sum(duplicated(clean_data))
```

# Data summary
```{r}
summary(clean_data)
```

# Check demographics
```{r}
# Gender
clean_data$gender <- factor(clean_data$gender, levels=c(1,2,3,4))
summary(clean_data$gender)
```

```{r}
# Education
clean_data$Edu <- factor(clean_data$Edu, levels=c(1,2,3,4,5))
summary(clean_data$Edu)
```

# Score data
```{r}
scored_data <- clean_data %>%
  mutate(across(c("PSS2", "PSS3"), ~{6 - .}),
         across(c("BSM1", "BSM3", "BSM7", "BSM8"), ~{8 - .}),
         mean_cra = rowMeans(select(., starts_with("CRA"))),
         mean_hcru = rowMeans(select(., starts_with("HCRU"))),
         mean_pss = rowMeans(select(., starts_with("PSS"))),
         mean_bsm = rowMeans(select(., starts_with("BSM"))),
         sum_cesd = rowSums(select(., starts_with("CES_D"))))%>%
         
  select(Age, SES, Edu, gender, mean_cra, mean_hcru,
         sum_cesd, mean_pss)
```

# Frequency table
```{r}
gender_freq <- scored_data %>% tabyl(gender)
levels(gender_freq$gender) <- c("male","female", "non-binary", "DWA")

edu_freq <- scored_data %>% tabyl(Edu)
levels(edu_freq$Edu) <- c("Elementary or lower","Highschool Diploma", "Bachelor's", "Master's", "PhD or higher")

frequencies<-edu_freq %>% #combine tables
add_row(Edu=gender_freq$gender, n = gender_freq$n, percent = gender_freq$percent) %>%
rename(Category = Edu)

apa_table(frequencies, caption = "Proportions of Education level and gender categories")
```


# Descriptives
- In the first step, the data are summarized to get the descriptive statistics. Subsequently, the data are reformatted.

```{r}
descriptives <- scored_data %>% 
  dplyr::summarize(across(c(SES, Age, mean_cra, mean_hcru,sum_cesd, 
                            mean_pss),
                   list(mean = mean, sd = sd, min = min, max = max)))%>%

  pivot_longer(everything(), names_to = "name") %>%
  
  separate(name, into = c("name","descriptive"), sep = "_(?=[^_]+$)")%>%
  
  pivot_wider(names_from = name, values_from = value) %>%
  
  rename(Summary = descriptive,
         CRA = mean_cra,  
         HCRU = mean_hcru,
         PSS = mean_pss,  
         CESD = sum_cesd)
```

# Calculate cronbach’s alphas
- Select the items from the raw data that belong to the specific scale.
- Calculate alpha and extract raw_alpha from the list the alpha function generates.

```{r}
alpha <- clean_data %>%
  dplyr::summarize(
            # Replication Block Alphas
            cra_alpha = select(.,starts_with("CRA")) %>% psych::alpha() %>%
              pluck("total", "raw_alpha"),
            hcru_alpha = select(.,starts_with("HCRU")) %>% psych::alpha() %>%
              pluck("total", "raw_alpha"),
            cesd_alpha = select(.,starts_with("CES_D")) %>% psych::alpha() %>%
              pluck("total", "raw_alpha"),
            pss_alpha = select(.,starts_with("PSS")) %>% psych::alpha(check.keys=TRUE) %>%
              pluck("total", "raw_alpha"))
```


```{r}
# add alphas as extra row to the descriptives table
descriptives <- descriptives %>%
  add_row(Summary = "alpha", SES = NA, CRA = alpha$cra_alpha,HCRU = alpha$hcru_alpha,PSS = alpha$pss_alpha, CESD = alpha$cesd_alpha)
```


```{r}
# make it a nicely formatted table
apa_table(descriptives)
```

# Plot monthly family income
```{r}
income_plot<-hist(scored_data$SES,
                  main="Family income distribution",
                  xlab="family income category")
```

# Mean centre all IVs for regressions with interaction terms
```{r}
centred_data <- scored_data %>%
  mutate(CRA_c = scale(mean_cra, center = TRUE, scale = FALSE),
         SES_c = scale(SES, center = TRUE, scale = FALSE),
         PSS_c = scale(mean_pss, center = TRUE, scale = FALSE),
         HCRU_c = scale(mean_hcru, center = TRUE, scale = FALSE))
```

# Regressions

# Main model
```{r}
#CRA and SES individually and the interaction between both
fit <- lm(sum_cesd ~ PSS_c + CRA_c + SES_c + CRA_c:SES_c, data = centred_data)
```

# Check model fit
```{r}
check_model(fit)
```

# Model summary
```{r}
summary(fit)
```

# Prettier summary with partial correlations
```{r}
# Fit 
# prettier summary with partial correlations
summ(fit, confint = TRUE, part.corr = TRUE)
```

# Simple slope analysis
```{r}
interactions::sim_slopes(fit, pred = CRA_c, modx=SES_c,modxvals = NULL, jnalpha = 0.05, digits = 3, n.sd = 1, jnplot = TRUE, confint = TRUE)
```

# Interaction plot
```{r}
# create interaction plot
interaction_plot <- interactions::interact_plot(model = fit,
                                                pred = CRA_c,
                                                modx = SES_c,
                                                interval=TRUE, 
                                                x.label = "Cognitive Reappraisal Ability",
                                                y.label= "Depressive Symptoms",
                                                legend.main = "family income")

interaction_plot
```

# Include covariates individually

```{r}
# HCRU
fit_2 <- lm(sum_cesd ~ PSS_c + CRA_c + SES_c + CRA_c:SES_c + HCRU_c, data = centred_data)
summ(fit_2, confint = TRUE, part.corr = TRUE)
```


```{r}
# Age
fit_3 <- lm(sum_cesd ~ PSS_c + CRA_c + SES_c + CRA_c:SES_c + Age, data = centred_data)
summ(fit_3, confint = TRUE, part.corr = TRUE)
```

# Simple slopes for fit_3: Age
```{r}
interactions::sim_slopes(fit_3, pred = CRA_c, modx=SES_c,modxvals = NULL, 
                         jnalpha = 0.05, digits = 3, n.sd = 1, jnplot = TRUE, confint = TRUE)
```


# Interaction plot for fit_3: Age
```{r}
# create interaction plot
interaction_plot_3 <- interactions::interact_plot(model = fit_3,
                                                pred = CRA_c,
                                                modx = SES_c,
                                                interval=TRUE, 
                                                x.label = "Cognitive Reappraisal Ability",
                                                y.label= "Depressive Symptoms",
                                                legend.main = "family income")

interaction_plot_3
```


```{r}
# Gender
fit_4 <- lm(sum_cesd ~ PSS_c + CRA_c + SES_c + CRA_c:SES_c + gender, data = centred_data)
summ(fit_4, confint = TRUE, part.corr = TRUE)
```

```{r}
# Education
fit_5 <- lm(sum_cesd ~ PSS_c + CRA_c + SES_c + CRA_c:SES_c + Edu, data = centred_data)
summ(fit_5, confint = TRUE, part.corr = TRUE)
```

```{r}
# Troy et al. (2017) also modeled one regression with race, however, the current study collected data from Iran without asking question about race. This is discussed in detail in the paper.
```


```{r}
# Troy et al. (2017) also modeled one regression without controlling for life stress (PSS)
fit_6 <- lm(sum_cesd ~ CRA_c + SES_c + CRA_c:SES_c, data = centred_data)

summ(fit_6, confint = TRUE, part.corr = TRUE)
```

# References
- Troy, A. S., Ford, B. Q., McRae, K., Zarolia, P., & Mauss, I. B. (2017). Change the things you can: Emotion regulation is more beneficial for people from lower than from higher socioeconomic status. Emotion, 17(1), 141–154. https://doi.org/10.1037/emo0000210

